Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-09-11 analysis/sim/run_simpw.Rmd
bugfix

## FORA
fo <- lapply(res,"[[",5)
fo2 <- prf(fo)
vioplot(fo2[["p"]],xlab="introduced noise",ylab="precision",main="fora") ; grid()
vioplot(fo2[["r"]],xlab="introduced noise",ylab="recall",main="fora") ; grid()
vioplot(fo2[["x"]],xlab="introduced noise",ylab="F1",main="fora") ; grid()

>>>>

## FORA
fo <- lapply(res,"[[",5)
fo2 <- prf(fo)
vioplot(fo2[["p"]],xlab="introduced noise",ylab="precision",main="fora") ; grid()
vioplot(fo2[["r"]],xlab="introduced noise",ylab="recall",main="fora") ; grid()
vioplot(fo2[["f"]],xlab="introduced noise",ylab="F1",main="fora") ; grid()
